More on the Slavnov products of spin chains, KP hierarchy tau and Baker-Akhiezer functions

### 2025-05-13 draft.tex
finish section 2

It has also been shown~\cite{Belliard:2019bfz} that if \(\det (\bm{M})
= 0 \) and \(\mathrm{rank}(\bm{M}) = n\), the Slavnov products are
given by
\begin{equation}
 \bm{\zeta}_\ell = \phi(\bm{v}) \tilde{\Delta}(\bm{u}_\ell)\hat{\Omega}_\ell\; . 
\end{equation}
Let us now explain the different terms in this expression. 
First of all, \(\phi(\bm{v})\) is a function of the Bethe roots and
\begin{equation}
  \tilde{\Delta}(\bm{u}_\ell) = \prod_{\substack{u_j, u_j \in \bm{u}_\ell \\ j>k}} \frac{c}{u_j - u_k}\; .
\end{equation}
We can absorbed the product of \(c\) into a new constant
\(c_0\), and it is easy to see that \(\tilde{\Delta}(\bm{u}_\ell)/c_0\) is the
inverse of the Vandermonde determinant \(\Delta(\bm{u}_\ell) =
\prod_{j>k}(u_j - u_k)\).

Additionally, the matrices \(\hat{\Omega}_\ell\) are minors of
\(\bm{\Omega}\) with the \(\ell\)-th column excluded, in other words,
\begin{equation}
 \hat{\Omega}_\ell = \det_{k\neq \ell} \Omega_{jk}\; ,
\end{equation}
where
\begin{equation}
  \Omega_{jk}(u_k; \bm{v}) = g(u_k, v_j) \mathcal{Y}(u_k; \{u_k, \bm{v}_j\})\; ,
  \quad j= 1, \dots, n\; , \quad k =1, \dots, n+1\; .
\end{equation}

All in all, we have an expression of the form
\begin{equation}
  \label{eq:slavnov-tau}
  \bm{\tau}_\ell(\bm{u}_\ell; \bm{v}) \equiv \frac{1}{c_0}\frac{\bm{\zeta}_\ell}{\phi(\bm{v})}
  = \frac{\hat{\Omega}_{\ell}}{\Delta(\bm{u}_\ell)} \; .
\end{equation}
This is the most important result for us, and our goal now is to show
that it is a tau-function of the KP-hierarchy.

>>>>

It has also been shown~\cite{Belliard:2019bfz} that for \(\det(\bm{M})
= 0\) and \(\mathrm{rank}(\bm{M}) = n\), the Slavnov products are
given by
\begin{equation}
 \bm{\zeta}_\ell = \phi(\bm{v}) \tilde{\Delta}(\bm{u}_\ell)\hat{\Omega}_\ell\; , \qquad \ell = 1, \dots, n+1\; .
\end{equation}
Let us now explain the different terms in this expression.  First of
all, \(\phi(\bm{v})\) is a function of the Bethe roots and its
particular form is not important in out analysis. Moreover, we have
\begin{equation}
  \tilde{\Delta}(\bm{u}_\ell) = \prod_{\substack{u_j, u_j \in \bm{u}_\ell \\ j>k}} \frac{c}{u_j - u_k}\; .
\end{equation}
We can also absorb the product of \(c\) into a new constant
\(c_0\), and it is easy to see that \(\tilde{\Delta}(\bm{u}_\ell)/c_0\) is the
inverse of the Vandermonde determinant \(\Delta(\bm{u}_\ell) =
\prod_{j>k}(u_j - u_k)\).

We now define the matrix \(\bm{\Omega}\) by specifying its components
\begin{equation}
  \Omega_{jk}(u_k; \bm{v}) = g(u_k, v_j) \mathcal{Y}(u_k; \{u_k, \bm{v}_j\})\; ,
  \quad j= 1, \dots, n\; , \quad k =1, \dots, n+1\; .
\end{equation}
The matrices \(\hat{\Omega}_\ell\) are minors of
\(\bm{\Omega}\) with the \(\ell\)-th column excluded, in other words,
\begin{equation}
 \hat{\Omega}_\ell = \det_{k\neq \ell} \Omega_{jk}\; . 
\end{equation}

All in all, we use these objects to define the \(n+1\) functions below
\begin{equation}
  \label{eq:slavnov-tau}
  \bm{\tau}_\ell(\bm{u}_\ell; \bm{v}) \equiv \frac{1}{c_0}\frac{\bm{\zeta}_\ell}{\phi(\bm{v})}
  = \frac{\hat{\Omega}_{\ell}}{\Delta(\bm{u}_\ell)} \; .
\end{equation}
This is the most important result for our discussion; and our goal now
is to show that it is a tau-function of the KP-hierarchy.
